### 2015-08-06 LaTeX/skewnormal.tex
updates to manuscript from Emeric and Dan

\begin{document}\linenumbers
\begin{center}
{\Large {\bf A spatial skew-$t$ model for threshold exceedances}}\\

{\large Samuel A Morris\footnote[1]{North Carolina State University}, Brian J Reich\footnotemark[1]{}, Emeric Thibaud\footnote[2]{Colorado State University}, and Dan Cooley\footnotemark[2]{}}

@@

\begin{abstract}
\singlespacing
To assess the compliance of air quality regulations, the Environmental Protection Agency (EPA) must know if a site exceeds a pre-specified threshold.
In the case of ozone, the threshold for compliance is fixed at 75 parts per billion, which is high, but not extreme at all locations.
We present a new method based on the spatial skew-$t$ process.
Our method incorporates a random partition to permit long-distance asymptotic independence while allowing for sites that are near one another to be asymptotically dependent, and we incorporate thresholding to allow the tails of the data to speak for themselves.
We also introduce a transformed AR(1) time-series to allow for temporal dependence.
Finally, our model allows for high-dimensional Bayesian inference that is comparable in speed to traditional geostatistical methods for large datasets.
We apply our method to an ozone analysis for July 2005, and find that our model does demonstrate some improvement over both Gaussian and max-stable methods in terms of predicting exceedances over a fixed threshold.

{\bf Key words}: Skew-$t$, random partition,
\end{abstract}

\newpage
\section{Introduction}\label{s:intro}
In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).

Traditional geostatistical modeling is based upon the assumption that observations come from a Gaussian process, a process that is fully defined by its mean and covariance functions.
In the limit of the Gaussian distribution, all observations are independent regardless of the strength of the correlation in the bulk of the data.
Furthermore, the Gaussian distribution is light-tailed and symmetric.
Therefore, it is inappropriate to use standard geostatistical methods when trying to describe dependence in the tails of the distribution.

Threshold modeling is popular in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Bivariate threshold models for extreme value distributions were considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a bivariate threshold in terms of only one or both components.
These threshold models were extended to spatial models for extremes by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to space-time modeling.
\citet{Engelke2014}, \citet{Wadsworth2014}, and \citet{Thibaud2013a} introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough that extremal models are valid for the data, and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high threshold, but on exceedances of a fixed threshold.

Instead, we propose a new spatiotemporal threshold exceedance model based on the skew-$t$ process \citep{Padoan2011}.
Our model is a threshold exceedance model for the multivariate skew-$t$ distribution that uses imputation for values below a fixed threshold.
We use a skew-$t$ distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed threshold at an unobserved location.

In a spatial setting, the multivariate skew-$t$ distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
This partition alleviates the asymptotic spatial dependence present in the skew-$t$ distribution for sites that are far apart.
Finally, our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models for large space-time datasets.

The paper is organized as follows.
Section \ref{s:spatialskew} is a brief review of the spatial skew-$t$ process.
In Section \ref{s:temporal}, we build upon the traditional skew-$t$ by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in Section \ref{s:comp}.
In Section \ref{s:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared Gaussian amd max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from throughout the US in section \ref{s:analysis}.
The final section provides brief discussion and direction for future research.

@@

\subsection{Skew-$t$ process} \label{s:skewt}
Let $Y(\bs)$ be the observation at spatial location $\bs = (s_1, s_2)$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial skew-$t$ process can be written
\begin{align}
  Y(\bs) = \bX(\bs)^T \bbeta + \lambda \sigma |z| + \sigma v(\bs)
\end{align}
where $\bX(\bs)$ is a set of spatial covariates at site $\bs$, $\bbeta$ is the vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skew, $z \sim N(0, 1)$, $\sigma^2 \sim \text{IG}(a, b)$ is an inverse gamma random variable, and $v(\bs)$ is a spatial Gaussian process with mean zero, variance one, and a positive definite correlation function.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^T$.
After marginalizing over both $z$ and $\sigma$,
\begin{align}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, 2a), \label{eq:fullmodel}
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta$, correlation matrix $\bOmega$, slant parameters $\balpha$ and degrees of freedom $2a$, where $\bX = [\bX(\bs_1)^T, \ldots, \bX(\bs_n)^T]$, $\bOmega = \bomega \bar{\bOmega} \bomega$, $\bomega = \text{diag}\left(\frac{1}{ \sqrt{ab}}, \ldots, \frac{1}{\sqrt{ab}}\right)$, $\bar{\bOmega} = (\bSigma + \lambda^2 \bOne \bOne^T$), $\balpha = \lambda (1 + \lambda^2 \bOne^T \bSigma^{-1} \bOne)^{-1/2} \bOne^T \bSigma^{-1}$, and $\bSigma$ is the positive definite correlation matrix of $[v(\bs_1), \ldots, v(\bs_n)]$.
Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \text{cor}[v(\bs), v(\bt)] = \gamma I(\bs = \bt) + (1 - \gamma)  \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right) \label{eq:matern}
\end{align}
where $\rho$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs - \bt ||$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $2a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.

\subsection{Extremal dependence}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for locations $\bs$ and $\bt$ separated by distance $h = || \bs - \bt ||$ with identical marginal distributions is
\begin{align}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs) > c | Y(\bt) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in Appendix \ref{a:skewt}).
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.

\section{Spatiotemporal skew-$t$ model for extremes}\label{s:spatial}
In this section, we propose extensions to the skew-$t$ process to model spatial extremes over a large geographic region by introducing censoring to focus on tail behavior and a random partition to remove long-range asymptotic dependence.
For notational convenience, we introduce the model for a single replication, and then extend this model to the spatiotemporal setting in Section \ref{s:temporal}.

\subsection{Censoring to focus on the tails}
Because one of our goals is to model the dependence of the distribution in the tails of the data, we choose to censor values below a threshold.
Let
\beq\label{Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
Then, assuming the uncensored data $Y(\bs)$ are observations from a skew-$t$ process, we update values censored below the threshold using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
The motivation for the partition is that for a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.
Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012} with a hybrid spatial dependence model.
\citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
Let $\bw = (w_1, w_2)$ be the location of a spatial knot.
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) = z_{k} \quad \text{and} \quad \sigma(\bs) = \sigma_{k} \label{eq:sitezsig}
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2 \iid$ IG$(a, b)$ where IG is the distribution function of an inverse gamma random variable.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

When incorporating the random partition, conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in (\ref{eq:chiskew-t}), $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
So, to show that $\lim_{h \rightarrow \infty} \chi(h) = 0$, we need only know that $\lim_{h \rightarrow \infty} \pi(h) = 0$. A proof of this is given in Appendix \ref{a:proofsamepartition}.

In Figure \ref{fig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and 3 degrees of freedom.
To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/chi-h.pdf}
  \caption{$\chi(h)$ for $K = 1, 3, 5$, and $10$ knots as a function of distance.}
  \label{fig:chi}
\end{figure}

@@

A plot of the relative Brier scores is given in Figure \ref{fig:simbrierscores}.
We find that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
One exception to this is the case when the generative process is max-stable.
In this case, the max-stable method outperforms our method; however, for predictions at high quantile levels, the differences between the max-stable method and our method decrease.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model used in the method.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides more flexibility for data that demonstrate some level of asymmetry or heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

\section{Data analysis}\label{s:analysis}
To illustrate this method, we consider 31 daily observations of maximum 8-hour ozone measurements for July 2005 at 1089 Air Quality System (AQS) monitoring sites in the United States as the response (see Figure \ref{fig:ozone}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression assuming a mean function of
\begin{align}
  \text{E}[Y_i(\bs)] = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{eq:datamean}
\end{align}
The data from July 10 are shown in Figure \ref{fig:ozone} along with a Q-Q plot of the residuals compared to a skew-$t$ distribution with 10 d.f. and $\alpha = 1$.
\begin{figure}
  \centering
  \includegraphics[width=0.56\linewidth]{plots/ozone-10jul-us.pdf}
  \includegraphics[width=0.41\linewidth]{plots/qq-res.pdf}
  \caption{Ozone values on 10 July 2005 (left) Q-Q plot of the residuals for a skew-$t$ distribution with 10 d.f. and $\alpha = 1$ (right)}
  \label{fig:ozone}
\end{figure}

>>>>

\begin{document}\linenumbers
\begin{center}
{\Large {\bf A space-time skew-$t$ model for threshold exceedances}}\\

{\large Samuel A Morris\footnote[1]{North Carolina State University}, Brian J Reich\footnotemark[1]{}, Emeric Thibaud\footnote[2]{Colorado State University}, and Daniel Cooley\footnotemark[2]{}}

@@

\begin{abstract}
\singlespacing
To assess the compliance of air quality regulations, the Environmental Protection Agency (EPA) must know if a site exceeds a pre-specified threshold.
In the case of ozone, the threshold for compliance is fixed at 75 parts per billion, which is high, but not extreme at all locations.
We present a new method based on the spatial skew-$t$ process.
Our method incorporates a random partition to permit long-distance asymptotic independence while allowing for sites that are near one another to be asymptotically dependent, and we incorporate thresholding to allow the tails of the data to speak for themselves.
We also introduce a transformed AR(1) time-series to allow for temporal dependence.
Finally, our model allows for high-dimensional Bayesian inference that is comparable in speed to traditional geostatistical methods for large datasets.
We apply our method to an ozone analysis for July 2005, and find that our model improves over both Gaussian and max-stable methods in terms of predicting exceedances over a fixed threshold.

{\bf Key words}: Skew-$t$, random partition, MCMC, extreme value analysis, spatio-temporal
\end{abstract}

\newpage
\section{Introduction}\label{s:intro}
In many climatological applications, researchers are interested in learning about the average behavior of different climate variables (e.g. ozone, temperature, rainfall).
Our study is motivated by an air pollution application where the focus is not on the average behavior, but instead the behavior over a fixed threshold determined by government regulation.
More specifically, we consider the case of compliance for ozone.
A site is said to be in compliance if the fourth highest daily maximum 8-hour concentration averaged over 3 years does not exceed 75 parts per billion (ppb).
Figure \ref{fig:ozone-10jul} shows the ozone levels from July 10, 2005, at 1089 stations across the United States.
We see a large area above the compliance level in the midwest covering Ohio, Indiana, Illinois, and parts of the surrounding states.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/ozone-10jul-us.pdf}
  \caption{Ozone values on July 10, 2005}
  \label{fig:ozone-10jul}
\end{figure}

A spatial model for threshold exceedances warrants special consideration and standard spatial methods are likely to perform poorly.
First, because we are interested only in high values, we want to ``let the tail speak for itself''.
That is, if we fit a model to the entire data set, low-to-moderate values would influence the fit of the overall model.
As there are more of these values, they can unduly influence the distribution at the higher levels about which we are interested.
Our inference method will only use data which exceed a threshold, and will impute data below the threshold, thereby tailoring the fit to the levels of interest.
Second, likelihood-based spatial modeling typically assumes a Gaussian process, which is appropriate when mean behavior is of interest.
However, the Gaussian distribution is light-tailed and symmetric, and therefore may be inappropriate for modeling data which does not share this tail behavior.
Third, we aim to capture the dependence structure when ozone is at high levels, and dependence at these levels may not be well-represented by covariances which focus again on mean behavior.
Asymptotic dependence/independence (see Section \ref{s:extdep}) are notions which describe how two random variables' dependence behaves as one looks further into the joint tail.
The Gaussian distribution always exhibits asymptotic independence, except in the case of perfect dependence, thus is an inappropriate model for data which exhibits asymptotic dependence.
To allow for more flexibility in the marginal tail and to allow for asymptotic dependence, the skew-$t$ distribution forms the basis for our model.

Our approach differs from threshold modeling approaches based on extreme value distributions.
There has been extensive work on threshold modeling in the field of extreme value statistics where extreme events are naturally defined in terms of exceedances over a high threshold.
\citet{Davison1990} considered modeling threshold exceedances of univariate time series by the generalized Pareto distribution.
Bivariate threshold models for extreme value distributions were considered by \citet{Ledford1996} who introduced a censored approach that provides a way to deal with different types of exceedances of a bivariate threshold in terms of only one or both components.
These threshold models were extended to spatial models for extremes by \citet{Wadsworth2012} and \citet{Thibaud2013} who fit various models to spatial extremes using a censored pairwise likelihood \citep{Padoan2010} based on the approach of \citet{Ledford1996}.
\citet{Huser2014} further extended this to space-time modeling.
\citet{Thibaud2013a}, \citet{Engelke2014}, and \citet{Wadsworth2014}, introduced more efficient inference for threshold exceedances of extremal spatial processes with full likelihood methods.
The previous approaches to threshold modeling are motivated by extreme value theory and assume the threshold is high enough that extremal models are valid for the data, and for extrapolation beyond the range of observed values.
Moreover, these approaches are computationally intensive and limited to rather small datasets.
For example, \citet{Wadsworth2014} present a simulation study with observations at 16 sites on a regular grid, and \citet{Engelke2014} analyze a dataset with observations at 35 meteorological stations.
Our application with ozone data does not fit into this framework because we do not focus on exceedances of a very high threshold, but on exceedances of a fixed threshold.
Furthermore, in our application, we have observations at over 1,000 ozone monitoring locations.

We propose a new spatiotemporal threshold exceedance model based on the skew-$t$ process \citep{Padoan2011}.
Our model is a threshold exceedance model for the multivariate skew-$t$ distribution for a fixed threshold.
In this setting, we describe the threshold as fixed because it is specified in advance by regulatory compliance.
This differs from the more traditional extremes literature where a threshold is selected to be the value beyond which an extremal model is appropriate for the data.
We use a skew-$t$ distribution because of its flexibility to model asymmetry and heavy-tailed data with the aim of predicting the probability of exceeding a high fixed threshold at an unobserved location.

Our model allows for inference and predictions using the full likelihood with computing on the order of Gaussian models for large space-time datasets.
This allows us to use Bayesian methods to impute data below the threshold as well as make predictions at unobserved locations.
In a spatial setting, the multivariate skew-$t$ distribution demonstrates asymptotic dependence between observations at all sites regardless of the distance between the sites.
In order to address this concern, we introduce a random spatial partition similar to the method used by \citet{Kim2005} for non-stationary Gaussian data.
This partition alleviates the asymptotic spatial dependence present in the skew-$t$ distribution for sites that are far apart.

The paper is organized as follows.
Section \ref{s:spatialskew} is a brief review of the spatial skew-$t$ process.
In Section \ref{s:spatial}, we build upon the traditional skew-$t$ process by incorporating censoring to focus on tails, partitioning to remove long-range asymptotic dependence, and extending the model to space-time data.
The computing is described in Section \ref{s:hier}.
In Section \ref{s:simstudy}, we present a simulation study that examines the predictive capabilities of this model compared Gaussian amd max-stable methods.
We then compare our method to Gaussian and max-stable methods with a data analysis of ozone measurements from 800 sites throughout the US in Section \ref{s:analysis}.
The final section provides brief discussion and direction for future research.

@@

\subsection{Skew-$t$ process} \label{s:skewt}
Let $Y(\bs)$ be the observation at spatial location $\bs$ in a spatial domain of interest $\calD \in \calR^2$.
The spatial skew-$t$ process can be written
\begin{align}
  Y(\bs) = \bX(\bs)^T \bbeta + \lambda \sigma |z| + \sigma v(\bs)
\end{align}
where $\bX(\bs)$ is a set of spatial covariates at site $\bs$, $\bbeta$ is the vector of regression parameters, $\lambda \in \calR$ is a parameter controlling skew, $z \sim N(0, 1)$, $\sigma^2 \sim \text{IG}(a, b)$ is random scale parameter, IG is the distribution function of an inverse gamma random variable, and $v(\bs)$ is a spatial Gaussian process with mean zero, variance one, and a positive definite correlation function.

For a finite collection of locations $\bs_1, \ldots, \bs_n$, denote the vector of observations $\bY = [Y(\bs_1), \ldots, Y(\bs_n)]^T$.
After marginalizing over both $z$ and $\sigma$,
\begin{align}
  \bY \sim \text{ST}_n(\bX \bbeta, \bOmega, \balpha, 2a), \label{eq:fullmodel}
\end{align}
that is, $\bY$ follows an $n$-dimensional skew-$t$ distribution with location $\bX \bbeta$, correlation matrix $\bOmega$, slant parameters $\balpha$ and degrees of freedom $2a$, where $\bX = [\bX(\bs_1)^T, \ldots, \bX(\bs_n)^T]$, $\bOmega = \bomega \bar{\bOmega} \bomega$, $\bomega = \text{diag}\left(\frac{1}{ \sqrt{ab}}, \ldots, \frac{1}{\sqrt{ab}}\right)$, $\bar{\bOmega} = (\bSigma + \lambda^2 \bOne \bOne^T$), $\balpha = \lambda (1 + \lambda^2 \bOne^T \bSigma^{-1} \bOne)^{-1/2} \bOne^T \bSigma^{-1}$, and $\bSigma$ is the positive definite correlation matrix of $[v(\bs_1), \ldots, v(\bs_n)]$.
This process is desirable because of its flexible tail that is controlled by the skewness parameter $\lambda$ and degrees of freedom $2a$.
Furthermore, the marginal distributions at each location also follow a univariate skew-$t$ distribution \citep{Azzalini2014}.

Although any positive definite correlation function could be used, we choose to use the stationary isotropic \Matern correlation with
\begin{align}
  \text{cor}[v(\bs_1), v(\bs_2)] = \gamma I(\bs_1 = \bs_2) + (1 - \gamma)  \frac{ 1 }{ \Gamma(\nu) 2^{ \nu - 1}} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right)^{\nu} K_{\nu} \left( \sqrt{2\nu} \frac{ h }{ \rho } \right) \label{eq:matern}
\end{align}
where $\rho$ is the spatial range, $\nu$ is the smoothness, $\gamma$ is the proportion of variance accounted for by the spatial variation, $K_\nu$ is a modified Bessel function of the second kind, and $h = || \bs_1 - \bs_2 ||$.

\subsection{Extremal dependence}\label{s:extdep}
Our interest lies in spatial dependence in the tail of the skew-$t$ process.
One measure of extremal dependence is the $\chi$ statistic \citep{Coles1999}.
For a stationary and isotropic spatial process, the $\chi$ statistic for locations $\bs$ and $\bt$ separated by distance $h = || \bs - \bt ||$ with identical marginal distributions is
\begin{align}
  \chi(h) = \lim_{c \rightarrow c^*} \Pr[Y(\bs) > c | Y(\bt) > c]
\end{align}
where $c^*$ is the upper limit of the support of $Y$.
If $\chi(h) = 0$, then observations are asymptotically independent at distance $h$.
For Gaussian processes, $\chi(h) = 0$ regardless of the distance $h$, so they are not suitable for modeling asymptotically dependent extremes.
Unlike the Gaussian process, the skew-$t$ process is asymptotically dependent (the explicit expression for $\chi(h)$ is given in Appendix \ref{a:skewt}).
However, one problem with the spatial skew-$t$ process is that $\lim_{h \rightarrow \infty} \chi(h) > 0$.
This occurs because all observations, both near and far, share the same $z$ and $\sigma$ terms.
Therefore, this long-range dependence feature of the skew-$t$ process is not ideal for spatial analysis of large geographic regions where we expect only local spatial dependence.
We propose a solution to this in Section \ref{s:part}.

\section{Spatiotemporal skew-$t$ model for threshold exceedances}\label{s:spatial}
In this section, we propose extensions to the skew-$t$ process to model spatial extremes over a large geographic region by introducing censoring to focus on tail behavior and a random partition to remove long-range asymptotic dependence.
For notational convenience, we introduce the model for a single replication, and then extend this model to the spatiotemporal setting in Section \ref{s:temporal}.

\subsection{Censoring to focus on the tails}
As mentioned previously, we propose to use a censored approach because we are interested in high values and do not want the low-to-moderate values to influence the fit of the overall model.
The censored observations below the threshold give information on the marginal probabilities to exceed the threshold and on the dependence, but their values are not used to fit the model.
Let
\beq\label{Yt}
  \widetilde{Y}(\bs) = \left\{ \begin{array}{ll}
      Y(\bs) \quad & \delta(\bs) = 1 \\
      T & \delta(\bs) = 0
  \end{array} \right.
\eeq
be the censored observation at site $\bs$ where $Y(\bs)$ is the uncensored observation, $\delta(\bs) = I[Y(\bs) > T]$, and $T$ is a pre-specified threshold value.
We impute the censored values as a step in the MCMC algorithm used to fit the model described in Section \ref{s:comp}.

\subsection{Partitioning to remove long-range asymptotic dependence}\label{s:part}
The motivation for the partition is that for a large spatial domain, it may not be reasonable to assume sites that are far apart demonstrate asymptotic dependence.
Modeling different levels of asymptotic dependence was discussed by \citet{Wadsworth2012} with a hybrid spatial dependence model.
\citet{Huser2014} also allow for varying asymptotic dependence across both space and time with a partition structure represented by random discs moving across the space for a random duration with a random velocity and random radius.
We handle the problem of long-range asymptotic dependence with a random partition.
As discussed in Section \ref{s:spatialskew}, the source of long-range dependence is the shared $z$ and $\sigma$.
Therefore, to alleviate this dependence, we allow $z$ and $\sigma$ to vary by site.
The model becomes
\begin{align} \label{eq:partition}
  Y(\bs) &= \bX(\bs)^T \bbeta + \lambda \sigma(\bs) |z(\bs)| + \sigma(\bs) v(\bs).
\end{align}
To model spatial variation, consider a set of spatial knots $\bw_1, \ldots, \bw_K$ from a homogeneous Poisson process with intensity $\mu$ over spatial domain $\calD \in \calR^2$.
The knots define a random partition of $\calD$ by subregions $P_{1}, \ldots, P_{K}$ defined as
\begin{align} \label{eq:subregions}
  P_{k} = \{ \bs : k = \argmin_\ell || \bs - \bw_{\ell} || \}.
\end{align}
All $z(\bs)$ and $\sigma(\bs)$ for sites in subregion $k$ are assigned common values
\begin{align}
  z(\bs) = z_{k} \quad \text{and} \quad \sigma(\bs) = \sigma_{k} \label{eq:sitezsig}
\end{align}
and the $z_k$ and $\sigma^2_k$ are distributed as $z_k \iid N(0, 1)$ and $\sigma^2_k \iid$ IG$(a, b)$.
So, within each partition, $Y(\bs)$ follows the spatial skew-$t$ process defined in Section \ref{s:spatialskew}.
Across partitions, the $Y(\bs)$ remain correlated via the correlation function for $v(\bs)$ because $v(\bs)$ spans all partitions.

The partitioning model remove long-range dependence. Conditional on knots $\bw_1, \ldots, \bw_K$, the $\chi$ statistic for two sites $\bs$ and $\bt$ in partitions $k_s$ and $k_t$ respectively is
\begin{align}
  \chi(h) &= I(k_s = k_t) \chi_{\text{skew-}t}(h) + I(k_s \neq k_t) \chi_{\text{Gaus}}(h) \nonumber \\
         &= I(k_s = k_t) \chi_{\text{skew-}t}(h)
\end{align}
where $I(\cdot)$ is an indicator function, $\chi_{\text{skew-}t}(h)$ is the $\chi$ statistic for a skew-$t$ process given in (\ref{eq:chiskew-t}), $\chi_{\text{Gaus}}(h)$ is the $\chi$ statistic for a Gaussian process, and $h = ||\bs - \bt||$.
Therefore, sites in different subregions are asymptotically independent because $\chi_{\text{Gaus}}(h) = 0$ for all $h$.
Marginally, over the knots, $\chi(h) = \pi(h) \chi_{\text{skew}-t}(h)$, where $\pi(h) = \Pr(k_s = k_t)$ is the probability that two sites separated by distance $h$ are in the same partition.
In Appendix \ref{a:proofsamepartition}, we show that $\lim_{h \rightarrow \infty} \pi(h) = 0$, implying $\lim_{h \rightarrow \infty} \chi(h) = 0$.
In Figure \ref{fig:chi}, we give $\chi(h)$ for $K = 1, 3, 5, 10$ partitions for a skew-$t$ distribution with $\alpha = 10$, and 3 degrees of freedom.
We estimate $\pi(h)$ through simulation.
% To estimate $\pi(h)$, we generate 500 sites uniformly over the unit-square.
% We then randomly generate 400 different sets of partitions using $K = 3$, $5$, and $10$.
% For each set of knots, we take $\pi(h)$ to be the proportion of sites in the same partition that are separated by distance $h$.
% This plot demonstrates how partitioning helps to reduce extremal dependence as $h$ increases.

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{plots/chi-h.pdf}
  \caption{$\chi$, as a function of distance, for $K = 1, 3, 5$, and $10$ knots.}
  \label{fig:chi}
\end{figure}

@@

The results show that when the data are generated from a Gaussian process, our method performs comparably to a Gaussian approach.
In general, when the underlying process is not Gaussian, our method results in an improvement over both the max-stable and Gaussian methods.
One exception to this is the case when the generative process is max-stable.
In this case, the max-stable method outperforms our method; however, for predictions at high quantile levels, the differences between the max-stable method and our method decrease.
The non-thresholded methods tend to outperform the thresholded methods, but this is not surprising given that in most cases, the data are generated directly from the model used in the method.
% Finally, for setting 5, although the thresholded version of the single-partition model tends to perform the best across all of the extreme quantiles, the difference between the thresholded and non-thresholded methods is no longer significant in the more extreme quantiles.
In summary, our method provides more flexibility for data that demonstrate some level of asymmetry or heavy tails, while still performing comparably to Gaussian methods when the data are symmetric and have light tails.

@@

\section{Data analysis}\label{s:analysis}
We consider daily observations of maximum 8-hour ozone measurements for the 31 days of July 2005 at 1,089 Air Quality System (AQS) monitoring sites in the United States as the response (see Figure \ref{fig:ozone-10jul}).
For each site, we also have covariate information containing the estimated ozone from the Community Multi-scale Air Quality (CMAQ) modeling system.
Initially, we fit a linear regression assuming a mean function of
\begin{align}
  \text{E}[Y_i(\bs)] = \beta_0 + \beta_1 \cdot \text{CMAQ}_t(\bs). \label{eq:datamean}
\end{align}
Figure \ref{fig:ozone-qq} shows a Q-Q plot of the residuals compared to a skew-$t$ distribution with 10 d.f. and $\alpha = 1$.
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{plots/qq-res.pdf}
  \caption{Q-Q plot of the residuals for a skew-$t$ distribution with 10 d.f. and $\alpha = 1$ (right)}
  \label{fig:ozone-qq}
\end{figure}
